Constraint Grammar as a SAT problem

### 2015-05-19 paper/nodalida2015.tex
stuff

Encoding CG in logic increases computational complexity, 
but as a tradeoff, it could simplify the grammar writing.
Due to representing the rules as implications, the requirement of being unambiguously tagged becomes irrelevant.
One rule corresponds to many logical formulas (each condition being
the target), making the number of the rules potentially smaller.
Ordering can be preserved or discarded; in the latter case, we solve
eventual rule conflicts by finding a solution that discards the least
number of rule applications.
% our experiments show that it is possible to write a small grammar, 
% which, when run with SAT-CG, disambiguates more than the same
%grammar run with VISL CG-3.

>>>>

Encoding CG in logic increases computational complexity, 
but as a tradeoff, it could simplify the grammar writing.
Due to representing the rules as implications, cautious context
condition becomes irrelevant.
One rule corresponds to many logical formulas (each condition being
the target), which makes the number of the rules potentially smaller.
Ordering can be preserved or discarded; in the latter case, we solve
eventual rule conflicts by finding a solution that discards the least
number of rule applications.
% our experiments show that it is possible to write a small grammar, 
% which, when run with SAT-CG, disambiguates more than the same
%grammar run with VISL CG-3.
